\section{Approximation Algorithms}
\label{sec:approx_algs}
\citet{kempe2003maximizing} proved that under both the \ltmodel{} and \icmodel{} models, an optimal solution to \infmax{} can be approximated
to within a factor of $\lrp{1 - \frac{1}{e} - \varepsilon}$, where $\varepsilon \in [0, 1 - \frac{1}{e}]$. The core of their argument is that
under these models, the influence function $\sigma$ satisfies the property of submodularity. 

\begin{definition}[Submodularity]
    Let $U$ be some universal set. A function $f\colon U \to \R$ is submodular if it satisfies 
    \begin{equation}
        \func{f}{A \cup \lrc{e}} - \func{f}{A} \geq  \func{f}{B \cup \lrc{e}} - \func{f}{B}
        \label{eq:submod}
    \end{equation} 
    for all sets $A \subseteq B \subseteq U$ and elements $e \in U \sm B$.
    \label{def:submod} 
\end{definition}
 
If it can be shown that $\sigma$ is non-negative, monotone (i.e.\! non-decreasing), and submodular for some diffusion model, then a result by \citet{nemhauser1978analysis} shows that a simple greedy algorithm for maximizing such a submodular function subject to a cardinality constraint gives a $\lrp{1 - \frac{1}{e}}$ approximation 
to the optimal solution \footnote{\cite{sviridenko2004note} gives a greedy algorithm with the same approximation ratio for the more general problem of maximizing a non-negative, monotone, submodular function under a knapsack constraint.}. 

\begin{theorem}[\cite{nemhauser1978analysis}]
    Consider a non-negative, monotone, submodular function $f$ and an integer $k$. Let $S^*$ be the set of size $k$ that maximizes $f$ (i.e.\! the optimal solution). 
    Let $S$ be the set constructed by iteratively choosing the $k$ elements that give the maximum marginal gain to the function value at each iteration, starting from the empty set. Then $\func{f}{S} \geq \lrp{1 - \frac{1}{e}}\func{f}{S^*}$. 
    \label{thm:submod_cardin}
\end{theorem}

A generalization of the above theorem, where the greedy algorithm iteratively picks elements within a factor of 
$(1-\varepsilon)$ of the largest marginal gain at each step gives a $(1 - \frac{1}{e} - \varepsilon^\prime)$ approximation, 
where $\varepsilon^\prime$ depends polynomially on $\varepsilon$. 

%As shown in \cref{sec:submod_cardin_modify}, the above greedy approach can be generalized
%to give a $\lrp{1 - \frac{1}{e} - \varepsilon}$ approximation to the optimal solution, where $\varepsilon \in [0, 1 - \frac{1}{e}]$. 

\subsection{Submodularity under the Independent Cascade Model}
Because of the probabilistic nature of $\sigma$, it is difficult to prove it is submodular directly. Instead, it is helpful to reformulate the problem in terms of \emph{realizations} of the underlying network.

\begin{definition}[Realization]
    A realization of a graph $G = \lrp{V, E}$ can be thought of as a mapping $\phi\colon E 
    \to \lrc{L, B}$, where edges are given a label $L$ if they are a \emph{live} edge and $B$ if they are a \emph{blocked} edge. A node can be considered active iff there is a path consisting of only live edges between it and another active node. 
    \label{def:realization}
\end{definition}

This defines a probability space of $2^m$ realizations, where each realization denotes a unique configuration of live and blocked edges. 
In the \icmodel{} model, an edge $\lrp{u, v}$ is live with probability $\func{p}{u,v}$ and blocked with probability $1 - \func{p}{u,v}$. 

\begin{theorem}
    For any instance of the \icmodel{} model, the influence function $\sigma$ is submodular.
    \label{thm:ic_submod}
\end{theorem}
\begin{proof}
    Consider some arbitrary realization $\phi$ of the network $G$. We can now define the function 
    $\varphi_{\phi}(S)$ that gives the number of active nodes in the realization $\phi$ by initially activating a seed set $S$. Note that this is in fact now a deterministic quantity because we have fixed our choice of $\phi$. Hence, $\func{\sigma_{\phi}}{S} = \EX{ \func{\varphi_{\phi}}{S} } = \func{\varphi_{\phi}}{S}$ is also deterministic. 
    
    We now show that $\sigma_{\phi}$ is submodular. Define $R(v, \phi)$ to be the set of nodes that have a direct path from node $v$ consisting of only live edges. Let $A, B$ be two seed node sets such that $A \subseteq B$ and $v$ a node not in $B$. With $A$, the addition of $v$ to it increases $\func{\sigma_{\phi}}{A}$ by $\abs{R(v, \phi) \sm \cup_{u\in A} R(u, \phi)}$, 
    and similarly with $B$ it increases $\func{\sigma_{\phi}}{B}$ by $\abs{R(v, \phi) \sm \cup_{u\in B} R(u, \phi)}$. However, since clearly $\cup_{u\in A} R(u, \phi) \subseteq \cup_{u\in B} R(u, \phi)$, the amount added to $\func{\sigma_{\phi}}{A}$ is at least the amount added to $\func{\sigma_{\phi}}{B}$. Hence, 
    \begin{equation*}
        \func{\sigma_{\phi}}{A \cup \lrc{v}} - \func{\sigma_{\phi}}{A} \geq \func{\sigma_{\phi}}{B \cup \lrc{v}} - \func{\sigma_{\phi}}{B}
    \end{equation*}
    which satisfies \cref{def:submod}. 
    
    Note that 
    \begin{equation*}
        \infl{S} = \sum_{\text{realizations } \phi} \Pr \lrp{\phi} \func{\sigma_{\phi}}{S}
    \end{equation*}
    since the expected number of active nodes at the end of a cascade starting from $S$ is just the weighted average of the number of active nodes found by activating $S$ over all realizations. Since a non-negative linear combination of submodular functions is also submodular, $\sigma$ is submodular. 
\end{proof}

\subsection{Submodularity under the Linear Threshold Model}
We again make use of the concept of realizations in \cref{def:realization}. 
However, in general, fixing a choice of threshold values does not guarantee that the influence 
function will be submodular. Thus, we require a different analysis compared to the \icmodel{} model.

In the \ltmodel{} model, an edge cannot be 
considered live or blocked independently of the status of other edges. Instead, at most one incoming edge 
for each node can be considered live. More formally, a node $v$ selects at most one its in-edges at random, where each edge
is chosen with probability $\f[w]{u, v}$ where $u \in \f[\Gamma]{v}$, or chooses no edge with probability 
$1 - \sum_{u \in \Gamma(v)} \f[w]{u,v}$ to be live. The rest of the edges are considered blocked.  

\begin{claim}
    For a seed set $S$, the following result in the same distributions over active sets of nodes: 
    \begin{enumerate}
        \item Running the Linear Threshold process to completion starting from $S$
        \item Creating realizations as defined above and initially activating $S$. 
    \end{enumerate}
\end{claim}
\begin{proof}
    We first consider the \ltmodel{} process. We can extend the notion of influence weight by defining 
    $\f[w]{u, v} = 0$ if $u \notin \f[\Gamma]{v}$. Define $S_t$ to be the set of active nodes at the end of iteration $t$, where $t = 0, 1, \ldots$ and $S_0 = S$. 
    If a node $v$ has not become active at the end of iteration $t$, the probability it becomes active at the end of iteration $t+1$
    is equal to the chance that the influence weights in $S_t \sm S_{t-1}$ push it over its threshold given that its threshold has not already been passed. 
    From a notational standpoint, this is equivalent to 
    \begin{align*}
        \Pr \lrp{\theta_v \leq \sum_{u \in S_t} \f[w]{u,v} \; \Biggl\lvert \; \theta_v > \sum_{u \in S_{t-1}} \f[w]{u,v}} &= 
        \frac{\Pr \lrp{\sum_{u \in S_{t-1}} \f[w]{u,v} < \theta_v \leq \sum_{u \in S_t} \f[w]{u,v}}}{\Pr \lrp{\theta_v > \sum_{u \in S_{t-1}} \f[w]{u,v}}}\\
        &=  \frac{\sum_{u \in S_t \sm S_{t-1}} \f[w]{u, v}}{1 - \sum_{u \in S_{t-1}} \f[w]{u, v}}
    \end{align*}
    since $\theta_v$ is sampled uniformly at random from $\lrb{0, 1}$.  

    We now consider the realization process, gradually revealing active nodes in iterations as in the \ltmodel{} model. Define $S_t$ for iterations $t = 0, 1, \ldots$ as before and additionally 
    define $S_t^\prime = S_t \sm S_{t-1}$ where $S_0^\prime = S_0$. Starting with $S_0^\prime$, for each node $v$ with at least one in-edge from 
    $S_0^\prime$, determine if $v$ has a live edge coming from this set. If so, then $v$ becomes active with $v \in S_1^\prime$; otherwise we keep the source 
    of $v$'s live in-edge (if it has one) unknown. Repeat this process starting from $S_1^\prime$, thus defining sets $S_2^\prime, S_3^\prime, \ldots$. 
    If $v$ has not become active at the end of iteration $t$, then the probability it is determined to be active at the end of iteration $t+1$ is equivalent 
    to the chance that its live edge comes from $S_t^\prime$ given that its live edge has not come from $S_0^\prime, \ldots, S_{t-1}^\prime$. 
    Namely, this probability is 
    \begin{equation*}
        \frac{\sum_{u \in S_t^\prime} \f[w]{u, v}}{1 - \sum_{u \in \cup_{i=0}^{t-1} S_i^\prime} \f[w]{u, v}} = \frac{\sum_{u \in S_t \sm S_{t-1}} \f[w]{u, v}}{1 - \sum_{u \in S_{t-1}} \f[w]{u, v}}. 
    \end{equation*}
    Since these probabilities are equivalent in both the \ltmodel{} model and realization process, we have the proof of the claim. 
\end{proof}

Since we have established that the notion of activations through realizations and live edge paths as defined before 
is equivalent to the \ltmodel{} model, we get the following theorem whose proof is identical to that of \cref{thm:ic_submod}. 
\begin{theorem}
    For any instance of the \ltmodel{} model, the influence function $\sigma$ is submodular. 
    \label{thm:lt_submod}
\end{theorem}
